Getting Started with the Graded Response Model (GRM): A gentle introduction and tutorial in R

### 2023-11-15 paper.qmd
quarto paper initiated

## Quarto

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

>>>>

```{r, echo=F, include=F}
#| label: setup
#| install.packages("tidyverse", "psych", "devtools", "mirt", "caret", dependencies=TRUE) 
#| INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed) ##

#| devtools::install_github("masurp/ggmirt")

#| Now, we activate the package:
library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)

```

{{< pagebreak >}}
